The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-06-08 doc/paper/paper2d.tex
Add figures.

@@

\begin{figure}
\figurenum{2}
\epsscale{0.9}
\plotone{layout.ps}
\figcaption{Schematic layout of one of the SDSS spectrographs, from the 
SDSS Project Book (http://www.astro.princeton.edu/PBOOK/spectro/spectro.htm).
Four main components are labeled: A) the slithead, B) the collimator, 
C) the beamsplitter, D) the grisms.
\label{fig2}
}
\end{figure}

@@

>>>>

\subsection{Tests of Spectrophotometry}

@@

\begin{figure}
\figurenum{2}
\epsscale{0.9}
\plotone{SpecSecFull.ps}
\figcaption{Schematic layout of one of the SDSS double-spectrographs.
The light is fed from 320 fibers entering at the slithead (A), which
is in the center of the beam in this Schmidt camera design.
\label{fig2}
}
\end{figure}

@@

\begin{figure}
\figurenum{10}
\epsscale{1.0}
\plotone{plot_bestthru.ps}
\figcaption{Throughput of the SDSS spectroscopic system,
as measured relative to the photon density expected above
the Earth's atmospheric by an aperture of 2.5-m with a 1.3-m
obscuration by the secondary mirror baffling.  These curves
are for plate 406 observed on MJD 51817.
Solid curves are for spectrograph \#1, and dotted curves
for spectrograph \#2.
\label{fig10}
}
\end{figure}
